Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-19 vesicle_code/docs/adhesion/revisions/reviewer2.tex
yny review2

\item\comment{In II. Governing equations and fig. 1: the right panel of the
figure and comments at the end of the section say that the part of
vesicle membranes that is out of the contact zone, including the parts
that are facing the outer fluid, experience an attractive interaction.
This is an artifact due to the long-range potential chosen by the
authors to model the interaction. In most experimental systems, the
adhesive forces leading to cluster formation are either due to direct
bridging of membranes or depletion phenomena that lead to osmotic
pressure gradients. This is the case for RBC aggregation for instance.
In both mechanisms, there is indeed no attractive force between membrane
parts that are out of the contact zone. It is perfectly fine to model
the interaction by an adhesion potential such as represented in fig 1
left, but its use introduces this artifact that should be acknowledged
by the authors. It is also due to the fact that the value of parameter
$\delta$ (the equilibrium distance) is not small compared to vesicle
dimensions. This is a numerical necessity to avoid the need to have
extremely refined meshes but again in experiments, the equilibrium
distance is usually much smaller that vesicle sizes and is more
comparable to molecular sizes (size of bridging molecules or of
depletion-inducing macromolecules). This deserves to be acknowledged
also, even though it may not impact too much the results.}
\begin{itemize}
  \item The referee is correct that vesicles outside of the contact zone
    do not feel a long range attractive interaction.  Our model follows
    the works on red blood cells by Flormann {\em et al.}~Scientific
    Reports (2017) and Hoore {\em et al.}~Soft Matter (2018).  In both
    these papers, the Lennard-Jones potential is used to model the
    adhesive interaction between red blood cells.  These models are
    found to be in good agreement with experiments and other models for
    adhesion (Ziherl and Svetina, PNAS (2017)).

@@

\item\comment{In the conclusions, an example of aggregation of vesicles enclosed
in a bigger one is presented. I do not think this brings much to this
paper. Why not keep this for a future paper dedicated to this specific
problem and instead show examples of aggregates without the enclosing
large vesicle? In what conditions (reduced volume, Hamaker constant)
can linear structures (rouleaux) be formed for instance (see the paper
by Hoore et al whose reference is given above for instance).}
\begin{itemize}
  \item We have removed this example from the manuscript.  Instead, we
    mention that future work includes a suspension of many vesicles.
\end{itemize}

>>>>

\item\comment{In II. Governing equations and fig. 1: the right panel of the
figure and comments at the end of the section say that the part of
vesicle membranes that is out of the contact zone, including the parts
that are facing the outer fluid, experience an attractive interaction.
This is an artifact due to the long-range potential chosen by the
authors to model the interaction. In most experimental systems, the
adhesive forces leading to cluster formation are either due to direct
bridging of membranes or depletion phenomena that lead to osmotic
pressure gradients. This is the case for RBC aggregation for instance.
In both mechanisms, there is indeed no attractive force between membrane
parts that are out of the contact zone. It is perfectly fine to model
the interaction by an adhesion potential such as represented in fig 1
left, but its use introduces this artifact that should be acknowledged
by the authors. It is also due to the fact that the value of parameter
$\delta$ (the equilibrium distance) is not small compared to vesicle
dimensions. This is a numerical necessity to avoid the need to have
extremely refined meshes but again in experiments, the equilibrium
distance is usually much smaller that vesicle sizes and is more
comparable to molecular sizes (size of bridging molecules or of
depletion-inducing macromolecules). This deserves to be acknowledged
also, even though it may not impact too much the results.}
\begin{itemize}
  \item The referee is correct that vesicles outside of the contact zone
    do not feel a long range attractive interaction.  Our model follows
    the works on red blood cells by Flormann {\em et al.}~Scientific
    Reports (2017) and Hoore {\em et al.}~Soft Matter (2018).  In both
    these papers, the Lennard-Jones potential is used to model the
    adhesive interaction between red blood cells.  
    Results from these modeling works are found to be in good agreement 
    with experiments and other models for adhesion (Ziherl and Svetina, PNAS (2017)).

@@

\item\comment{In the conclusions, an example of aggregation of vesicles enclosed
in a bigger one is presented. I do not think this brings much to this
paper. Why not keep this for a future paper dedicated to this specific
problem and instead show examples of aggregates without the enclosing
large vesicle? In what conditions (reduced volume, Hamaker constant)
can linear structures (rouleaux) be formed for instance (see the paper
by Hoore et al whose reference is given above for instance).}
\begin{itemize}
  \item We have removed this example from the manuscript.  We thank the referee for the great suggestion to examine the conditions for formation of
  linear structures. We have added a few new results in the revision and consequently we
    mention that future work includes a suspension of many vesicles.
\end{itemize}
